### 2018-07-17 paper/security-discussion.tex
WIP adapts SPOR security discussion

Bob constructs \iac{SPOR} route that he gives to Alice.
Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that might be Bob's device.
Alice will construct her own \ac{SPOR} route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
If we assume that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} global set of devices %Global Device Retinue 
(we will return to this assumption 
below), then their probability of successful attack is proportional to their 
size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).

>>>>

Bob constructs a Sphinxes route that he gives to Alice.
Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that device might be under Bob's 
control.
Instead, Alice will construct her own Sphinxes route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
This assumes that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} global set of devices.
If this is true, the probability of successful attack is proportional to the 
adversary's size in the network, \ie \(\frac{|D_i|}{|D|}\).
The adversary must be present on each layer and be selected on the first layer 
(which is lower-bounded by \(\frac{1}{w_L}\)) --- since after that the 
adversary can select its own nodes in the next layer instead of uniformly at 
random.
